\documentclass{resume} % Use the custom resume.cls style

\usepackage[left=0.4 in,top=0.4in,right=0.4 in,bottom=0.4in]{geometry} % Document margins
\newcommand{\tab}[1]{\hspace{.2667\textwidth}\rlap{#1}} 
\newcommand{\itab}[1]{\hspace{0em}\rlap{#1}}
\name{Rhyss Vivian} % Your name
% You can merge both of these into a single line, if you do not have a website.
\address{+1(907) 317-2469 \\ Anchorage, AK} 
\address{\href{mailto:rhyssv@gmail.com}{rhyssv@gmail.com} \\ \href{www.linkedin.com/in/rhyss-vivian}{linkedin.com/in/rhyss-vivian} \\ \href{www.northof66.com}{www.northof66.com}}  %

\begin{document}

%----------------------------------------------------------------------------------------
%	OBJECTIVE
%----------------------------------------------------------------------------------------

\begin{rSection}{OBJECTIVE}

{Cloud and Network Engineer with a background in large enterprises. }


\end{rSection}
%----------------------------------------------------------------------------------------
%	EDUCATION SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{Education}

{\bf BBA, Management Information Systems}, University of Alaska Anchorage \hfill {2015}\\
Relevant Coursework: A, B, C, and D.

\end{rSection}

%----------------------------------------------------------------------------------------
% TECHINICAL STRENGTHS	
%----------------------------------------------------------------------------------------
\begin{rSection}{SKILLS}

\begin{tabular}{ @{} >{\bfseries}l @{\hspace{6ex}} l }
Hardware & Cisco, Fortinet, Juniper, HPE, Dell\\
Clouds & Azure GCC-High\\
Software & Terraform, GitHub, Python\\
Certifications & CCNP: Security, Azure Administrator, Sec+\\
\end{tabular}\\
\end{rSection}

\begin{rSection}{EXPERIENCE}

\textbf{Cloud Engineer} \hfill Aug 2018 - Present\\
Chugach Government Solutions \hfill \textit{Anchorage, AK}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Created and enforced multi-cloud governance documentation.
     \item Lead technologist for Cloud, Networking, and Operations.
     \item Designed, planned, and implemented 30+ site Fortinet SD-WAN.
 \end{itemize}
 
\textbf{Network Administrator III} \hfill Sep 2014 - July 2018\\
Ukpeagvik Inupiat Corporation \hfill \textit{Anchorage, AK}
 \begin{itemize}
    \itemsep -3pt {} 
     \item Achieved X\% growth for XYZ using A, B, and C skills.
     \item Led XYZ which led to X\% of improvement in ABC
    \item Developed XYZ that did A, B, and C using X, Y, and Z. 
 \end{itemize}

\end{rSection} 

%----------------------------------------------------------------------------------------
%	WORK EXPERIENCE SECTION
%----------------------------------------------------------------------------------------

\begin{rSection}{PROJECTS}
\vspace{-1.25em}
\item \textbf{Azure/Microsoft365 Gov-Cloud Migration} {Built a tool to search for Hiring Managers and Recruiters by using ReactJS, NodeJS, Firebase and boolean queries. Over 25000 people have used it so far, with 5000+ queries being saved and shared, and search results even better than LinkedIn! \href{https://hiring-search.careerflow.ai/}{(Try it here)}}
\item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
\item \textbf{Short Project Title.} {Build a project that does something and had quantified success using A, B, and C. This project's description spans two lines and also won an award.}
\end{rSection} 

%----------------------------------------------------------------------------------------
\begin{rSection}{Extra-Curricular Activities} 
\begin{itemize}
    \item 	Actively write \href{https://www.faangpath.com/blog/}{blog posts} and social media posts (\href{https://www.tiktok.com/@faangpath}{TikTok}, \href{https://www.instagram.com/faangpath/?hl=en}{Instagram}) viewed by over 20K+ job seekers per week to help people with best practices to land their dream jobs. 
    \item	Sample bullet point.
\end{itemize}


\end{rSection}

%----------------------------------------------------------------------------------------
\begin{rSection}{Leadership} 
\begin{itemize}
    \item Admin for the \href{https://discord.com/invite/WWbjEaZ}{FAANGPath Discord community} with over 6000+ job seekers and industry mentors. Actively involved in facilitating online events, career conversations, and more alongside other admins and a team of volunteer moderators! 
\end{itemize}


\end{rSection}


\end{document}
